Generating the Blueprints of the Java Ecosystem

### 2015-02-26 msr.tex
working on text

Software metrics provide a means to extract useful and measurable information about the structure of a software system. Since software artifacts consist of digital data, many of their aspects can be easily measured. This is exemplified by the early appearance of metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code). Over the years, a wealth of different metrics have appeared in the literature. In addition, many of them, such as Chidamber and Kemerer's~\cite{CHKE94} and the metrics presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools.

@@

Maven is a build automation tool used primarily for Java projects, and it is hosted by the Apache Software Foundation~\cite{MAVEN}. To describe the software project being built, its dependencies on other libraries, and the build order Maven uses {\sc xml}. The repository contains more than 400,000 {\sc jar}s, in a variety of languages that are all using the {\sc jvm} platform as basis. These languages include Java, Clojure, Groovy, and Scala.

\begin{figure}
\centering
\includegraphics[scale=0.5]{import-process}
\caption{The dataset construction process}
\label{fig:dataset-construction}
\end{figure}

The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}. Initially, a snapshot of the Maven repository was downloaded locally. The repository contains various projects and their releases. We identified only the Java projects. The repository contains several versions of each project. All versions were filtered out and only the latest was kept. Each project consists of two {\sc jar} files, one that contains a compiled version of the project and one with the source code. We

@@

Table~\ref{tbl:selected-metrics} presents the key metrics that are calculated and stored in the dataset. Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics. Several metrics are calculated by more than one tools in this dataset, like \textit{cyclomatic complexity}, which is calculated by both \textit{clmt} and \textit{ckjm}. Both calculation are stored and provided by the dataset.Three tools were selected.

@@

@@

Figure~\ref{fig:database-schema} illustrates the database schema. The data were stored in a straightforward manner. The database schema consists of five tables; \textit{measurement}, \textit{category}, \textit{identifiers}, \textit{measurement\_type}, and \textit{project}. The central table is \textit{measurement}, which holds the actual measurement values. The other tables are used as normalization tables.

Metrics are divided into six categories that defined its scope; \textit{module}, \textit{class}, \textit{method}, \textit{code unit}, and \textit{project-wide}. These values are stored in \textit{category} table.

The descriptive names for each metric are stored in the \textit{measurement\_type} database table. There are 65 metrics available in the dataset. The names are composed by the actual metric name and the tool that was used to calculate them e.g. \textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity from the {\sc clmt} tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the {\sc ckjm} tool.

Filenames, method, class and package names along with other identifiers are stored in the \textit{identifiers} table. Note that each measurement has a related filename and a related identifier that points to the software element that is related e.g. the \textit{afferent coupling} metric for the module in the directory ``com/scalagent/jmx'' is related with the identifier \textit{com.scalagent.jmx}.

Finally the table \textit{project} contains the related project identifiers, extracted from the maven repository.

@@

@@

>>>>

Software metrics provide a means to extract useful and measurable information about the structure of a software system. Software development artifacts consist of digital data, many of their aspects can be easily measured. This is exemplified by the early appearance of metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code). Over the years, a wealth of different metrics have appeared in the literature. Many of them, such as Chidamber and Kemerer's~\cite{CHKE94} and the metrics presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools.

@@

Maven is a build automation tool used primarily for Java projects, and it is maintained by the Apache Software Foundation~\cite{MAVEN}. To describe the software project being built, its dependencies on other libraries, and the build order Maven uses {\sc xml}. The central repository contains more than 400,000 {\sc jar}s, in a variety of languages that are all using the {\sc jvm} platform as their runtime environment. These languages include Java, Clojure, Groovy, and Scala.

\begin{figure*}
\centering
\includegraphics[scale=0.7]{import-process}
\caption{The dataset construction process}
\label{fig:dataset-construction}
\end{figure*}

The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}. Initially, a snapshot of the Maven repository was downloaded locally. The repository contains various projects and their releases. We identified only the Java projects. The repository contains several versions of each project. All versions were filtered out and only the latest was kept. Each project consists of two {\sc jar} files, one that contains a compiled version of the project and one with the source code. The projects that did not had both binary and source jars, were excluded from the experiment.

When the selection process was finished, the {\sc jars} were downloaded from the central repository and with the help of a queue, delivered into a series of workers, which executed the tools and provided a series of measurements stored in {\sc json} form. The result files were validated by scripts and then the data were imported in a MySQL database.

@@

Three tools were selected to calculate the measurements.

@@

Table~\ref{tbl:selected-metrics} presents the key metrics that are calculated and stored in the dataset. Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics. Several metrics are calculated by more than one tool, like \textit{cyclomatic complexity}, which is calculated by both \textit{clmt} and \textit{ckjm}. Both calculations are available in the database.

A series of secondary metrics are also stored in the database. For example, a set of metrics that count the usage of specific {\sc dsl} application libraries in a software project. These are not included in the Table~\ref{tbl:selected-metrics}, since they are not commonly accepted. In Section~\ref{sec:dsl}, we describe a small experiment based on these metrics that measures the popularity of {\sc dsl} usage for the dataset anf therefore for the Java ecosystem in general.

@@

Figure~\ref{fig:database-schema} illustrates the database schema. It consists of five tables; \textit{measurement}, \textit{category}, \textit{identifiers}, \textit{measurement\_type}, and \textit{project}. The central database table is \textit{measurement}, which holds the measurement values. The other tables are used for normalization.

Metrics are divided into six categories that define their scope; \textit{module}, \textit{class}, \textit{method}, \textit{code unit}, and \textit{project-wide}. These values are stored in \textit{category} database table.

The descriptive names for each metric are stored in the \textit{measurement\_type} database table. There are 65 metrics available in the dataset. The names are composed by the actual metric name and the tool that was used to calculate them e.g. \textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity from the \textit{clmt} tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the \textit{ckjm} tool.

Filenames, methods, classes and package names along with other identifiers are stored in the \textit{identifiers} table. Note that each measurement has a related filename and a related identifier that points to a software element e.g. the \textit{afferent coupling} metric for the module in the directory ``com/scalagent/jmx'' is related with the identifier \textit{com.scalagent.jmx}.

Finally, the database table \textit{project} contains the related project identifiers, extracted from the maven repository.

@@

The measurements provided by this dataset, can be exploited in many

@@

Along with the
